---
title: "Ex-12 - Traveling Saleman Problem"
author: "Alberto Maximiliano Correa Pietrobon"
output: html_document
---
# Definicion del Problema
1.Try to solve the TSP with a LP matching model Use the scipy linprog package For the cities coordinates
use random points.  
2.Plot the resulting network with the matplotlib library.  
3.Understand the outputs What happend to the optimal path.
4.What are the alternatives to this formulation and their disadvantages  

```{r setup, include=FALSE}
rm( list=ls() )
gc()
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
```

```{r}

WishList<-c("Australia","France","china","Canada","Morocco")
#Matriz Distancias y NN 
Md<-matrix(nrow = 5, ncol = 5)
Mnn_R<-matrix(nrow = 5, ncol = 5)
rownames(Mnn_R)=colnames(Mnn_R)=WishList
CV<-c()
set.seed(1979)
for (i in 1:5) {
  for (j in 1:5) {
      if (i==j) {
          Md[i,j]=0
          Mnn_R[i,j]=0
          } else {
          
          Md[i,j]=Md[j,i]=runif(1, min=0, max=100) #esta se la dedico a Python
          CV<-cbind(CV,Md[i,j])
          Mnn_R[i,j]=1
        }
      }
}

#Creo Dataset vacio
TSP_R <- data.frame(Pais_O=character(),
                 Pais_D=character(),
                 Distancia=double(),
                 stringsAsFactors=FALSE)

str(TSP_R)

#Completo Dataset
k<-0
for (i in 1:length(WishList)) {
  for (j in 1:length(WishList)) {
      k<-k+1
      TSP_R[k,"Pais_O"]=WishList[i]
      TSP_R[k,"Pais_D"]=WishList[j]
      TSP_R[k,"Distancia"]=Md[i,j]
      }
}

```

```{python ImportPyLibraries}
import numpy as np
from scipy.optimize import linprog
```
## Defino Funcion Matriz NodoNodo a NodoArco
```{python Fc_NN2NA}
def nn2na (NN):
  #get every location where exist an arc:
  idxs = np.argwhere(NN)
  #idxs <-retorna un vector c con las posiciones ij con todos los arcos [(i1,j1),(i2,j2),etc]
  #Preallocate NA matrix, dimension is (nodes, arcs)
  NA = np.zeros([NN.shape[0],idxs.shape[0]]).astype(int)
  # Dimension de NA : Filas = dim NN (cantidad de nodos), COL= dim idxs (cantidad de arcos)
  
  #loop in every arc, complete from (1) to (-1)
  for i, arc in enumerate (idxs):
    NA[arc[0],i] = 1 #from
    NA[arc[1],i] = -1 #to
    
  #arc_idxs = [(arc[0], arc[1])] for arc in idxs]
  
  return NA
```
## Detallo el Modelo en terminos de Inv Operativa
```{python}
NN = r.Mnn_R
print(NN)
Aeq_i = nn2na(NN)
print(Aeq_i)
```
```{r}
Aeq_R<-(py$Aeq_i)
dim(Aeq_R)

Aeq_Pr<-matrix(nrow = nrow(Aeq_R), ncol = ncol(Aeq_R))
Aeq_Nr<-matrix(nrow = nrow(Aeq_R), ncol = ncol(Aeq_R))

for (i in 1:nrow(Aeq_R)) {
  for (j in 1:ncol(Aeq_R)) {
    if (Aeq_R[i,j]==1) {Aeq_Pr[i,j]=1; Aeq_Nr[i,j]=0}
    if (Aeq_R[i,j]==-1) {Aeq_Nr[i,j]=1; Aeq_Pr[i,j]=0}
    if (Aeq_R[i,j]==0) {Aeq_Pr[i,j]=0; Aeq_Nr[i,j]=0}
  }
}

#Concatenacion Aeq_Pr con Aeq_Nr
Aeq_Fr<-rbind(Aeq_Pr,Aeq_Nr)

#Creacion Vector beq
beq_r<-c(rep(1, times=ncol(Aeq_Fr)))
```

```{python}
C=np.array(r.CV)
print(C)
C = np.squeeze(np.asarray(r.CV))
print(C)
Aeq=r.Aeq_Fr
#print(Aeq)
#beq=np.array([1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1])
beq=np.squeeze(np.asarray(r.beq_r))
print(beq)
bounds = tuple ([(0,None) for i in range (0, Aeq.shape[1])])

print ('## inputs del optimizador ## \n'
       'Vector de Costos: %s \n'
       'A_eq Matriz Nodo-Arco: %s \n'
       'b_eq Vector b: %s \n'
       'Bounds of each X arc variable: %s \n' % (C,Aeq, beq,bounds))
```
```{python}
SP = linprog(C,A_eq=Aeq, b_eq=beq,bounds=bounds,method='simplex')
print(SP)
```